full title

### 2020-10-29 paper/pldi21/combined.tex
Changed: lazy concrete execution -> sealed symbolic execution

In this section, we formally define the combined analysis with lazy concrete
execution.  We extend the formalization of abstract interpretation and analysis
sensitivity proposed by \citet{sens-toplas}.

@@

\subsection{Lazy Concrete Execution}

We define a \textit{lazy concrete execution} by extending the transition
relation $\trans$ as a symbolic transition relation $\symbtrans$ on symbolic
states. First, we extends the concrete states $\stset$ to \textit{symbolic
states} with symbolic values $\symbset$ that denote abstract values that cannot be
concretized to singleton values. A symbolic transition relation $\symbtrans
\subseteq \symbstset \times (\symbstset \uplus \{ \excst \})$ is exactly the same
with the original transition relation $\trans$ except when the relation requires
the exact value of symbolic values.  In this case, the symbolic state has the
relation a special exception state $\excst$ to represent that it is impossible
to interpret in a concrete way.  Thus, a symbolic state \textit{always} has a
symbolic transition relation with a single symbolic state, and the lazy concrete
execution is linear until reaching the exception state.

@@

We define the \textit{combined analysis} of the abstract interpretation and the
lazy concrete execution.  In the combined analysis, we use the powerset of
symbolic states as the domain $\combdom = \powerset{\symbstset}$, and extend the
view transition as follows:
\[
  \begin{array}{l}
    \combviewtrans{\view}{\view'}(\combelem) =\\
    \qquad \{
      \symbst' \mid \symbst \in S \wedge
      \symbst \symbtrans \symbst' \wedge
      \saconverter(\symbst') = (\view', \_)
    \}\\
    \qquad \cup \left\{
    \begin{array}{ll}
      \{ \asconverter \circ \viewtrans{\view}{\view'}(\bigjoin D) \}
      & \text{if} \; D \neq \varnothing\\
      \varnothing & \text{otherwise}\\
    \end{array}
    \right.
  \end{array}
\]
where $S = \combelem\mid_{\checker}$ and $D =
\dot{\saconverter}(\combelem\mid_{\neg\checker})$.  The dot notation $\dot{f}$
denotes the element-wise extended function of a function $f$.  We could
configure when the lazy concrete execution or the abstract interpretation
is performed based on the definition of the $\checker$ function and its negation
$\neg\checker$.  It should satisfy the following condition for the soundness and
the termination of the combined analysis:
\[
  \checker(\symbst) \Rightarrow \symbst \symbtrans^k \excst \wedge
  1 < k \leq N
\]
where $N$ is a pre-defined maximum length of the lazy concrete execution.
The combined analysis just performs one-step symbolic transition for each
symbolic state that passes the filter $\checker$. On the other hand, it converts
remaining symbolic states to the corresponding abstract states, merges them into
a single abstract state, and performs the abstract one-step execution for the
abstract state.

>>>>

In this section, we formally define the combined analysis with sealed symbolic
execution.  We extend the formalization of abstract interpretation and analysis
sensitivity proposed by \citet{sens-toplas}.

@@

\subsection{Sealed Symbolic Execution}

We define a \textit{sealed symbolic execution} by extending the transition
relation $\trans$ as a symbolic transition relation $\symbtrans$ on symbolic
states. First, we extends the concrete states $\stset$ to \textit{symbolic
states} with symbolic values $\symbset$ that denote abstract values that cannot be
concretized to singleton values. A symbolic transition relation $\symbtrans
\subseteq \symbstset \times (\symbstset \uplus \{ \excst \})$ is exactly the same
with the original transition relation $\trans$ except when the relation requires
the exact value of symbolic values.  In this case, the symbolic state has the
relation a special exception state $\excst$ to represent that it is impossible
to interpret in a concrete way.  Thus, a symbolic state \textit{always} has a
symbolic transition relation with a single symbolic state, and the sealed
symbolic execution is linear until reaching the exception state.

@@

We define the \textit{combined analysis} of the abstract interpretation and the
sealed symbolic execution.  In the combined analysis, we use the powerset of
symbolic states as the domain $\combdom = \powerset{\symbstset}$, and extend the
view transition as follows:
\[
  \begin{array}{l}
    \combviewtrans{\view}{\view'}(\combelem) =\\
    \qquad \{
      \symbst' \mid \symbst \in S \wedge
      \symbst \symbtrans \symbst' \wedge
      \saconverter(\symbst') = (\view', \_)
    \}\\
    \qquad \cup \left\{
    \begin{array}{ll}
      \{ \asconverter \circ \viewtrans{\view}{\view'}(\bigjoin D) \}
      & \text{if} \; D \neq \varnothing\\
      \varnothing & \text{otherwise}\\
    \end{array}
    \right.
  \end{array}
\]
where $S = \combelem\mid_{\checker}$ and $D =
\dot{\saconverter}(\combelem\mid_{\neg\checker})$.  The dot notation $\dot{f}$
denotes the element-wise extended function of a function $f$.  We could
configure when the sealed symbolic execution or the abstract interpretation
is performed based on the definition of the $\checker$ function and its negation
$\neg\checker$.  It should satisfy the following condition for the soundness and
the termination of the combined analysis:
\[
  \checker(\symbst) \Rightarrow \symbst \symbtrans^k \excst \wedge
  1 < k \leq N
\]
where $N$ is a pre-defined maximum length of the sealed symbolic execution.
The combined analysis just performs one-step symbolic transition for each
symbolic state that passes the filter $\checker$. On the other hand, it converts
remaining symbolic states to the corresponding abstract states, merges them into
a single abstract state, and performs the abstract one-step execution for the
abstract state.

### 2020-10-29 paper/pldi21/motivation.tex
Changed: lazy concrete execution -> sealed symbolic execution

In this section, we first point out limitations that existing techniques face to
analyze the real-world example described in Figure~\ref{fig:example}.
We then show how our combined analysis increase the analysis scalability and
precision through lazy concrete execution, seamlessly combined with the original
static analysis.

@@

Dynamic analysis is still applicable using lazy concrete execution even if the
arguments are not concrete values.  The \jscode{getData} function is another
part to use \jscode{concat} function but we can only partially apply dynamic
analysis in this case.  It is invoked when loading more Zoom events in
``Webinars \& Events'' page.  At the first time, initial eight events are stored
in \jscode{this.pastEvents}.  For each click of the ``Load More'' button, the
\jscode{getData} sends a POST request to the server and receives additional
event information \jscode{e} in line 24.  Then, eight events in
\jscode{e.events} are appended to \jscode{this.pastEvents} using the
\jscode{concat} function in line 27-28.  In this case, arguments are not
deterministic but dependent on the given data from the server.  However, we know
that the number of arguments are still deterministically defined as \jscode{2}
and they are array objects.  Thus, we just invoke the funciton \jscode{concat}
with \jscode{\_} as \jscode{this} value and two abstract arrays as arguments for
dynamic analysis.  Then, dynamic analysis is successfully performed in line 2-8
because it just checks the length of \jscode{arguments} and passes its elements
to \jscode{array} and \jscode{args}.  Moreover, \jscode{isArray(array)} is also
able to be evaluated using concrete semantics because we know that \code{array}
is an abstract array.  Only copying via \jscode{copyArray}, flattening via
\jscode{baseFlatten}, and pushing via \jscode{arrayPush} utilize the abstract
semantics.  This is the core idea of lazy concrete execution to maximize the
part of dynamic analysis during static analysis.

In the remaining section we formally define the combined analysis with lazy
concrete execution in Section~\ref{sec:formal}.  Then, we explain how to define
the combined analysis for JavaScript programs in Section~\ref{sec:javascript}.

>>>>

In this section, we first point out limitations that existing techniques face to
analyze the real-world example described in Figure~\ref{fig:example}.
We then show how our combined analysis increase the analysis scalability and
precision through sealed symbolic execution, seamlessly combined with the original
static analysis.

@@

Dynamic analysis is still applicable using sealed symbolic concrete execution even if the
arguments are not concrete values.  The \jscode{getData} function is another
part to use \jscode{concat} function but we can only partially apply dynamic
analysis in this case.  It is invoked when loading more Zoom events in
``Webinars \& Events'' page.  At the first time, initial eight events are stored
in \jscode{this.pastEvents}.  For each click of the ``Load More'' button, the
\jscode{getData} sends a POST request to the server and receives additional
event information \jscode{e} in line 24.  Then, eight events in
\jscode{e.events} are appended to \jscode{this.pastEvents} using the
\jscode{concat} function in line 27-28.  In this case, arguments are not
deterministic but dependent on the given data from the server.  However, we know
that the number of arguments are still deterministically defined as \jscode{2}
and they are array objects.  Thus, we just invoke the funciton \jscode{concat}
with \jscode{\_} as \jscode{this} value and two abstract arrays as arguments for
dynamic analysis.  Then, dynamic analysis is successfully performed in line 2-8
because it just checks the length of \jscode{arguments} and passes its elements
to \jscode{array} and \jscode{args}.  Moreover, \jscode{isArray(array)} is also
able to be evaluated using concrete semantics because we know that \code{array}
is an abstract array.  Only copying via \jscode{copyArray}, flattening via
\jscode{baseFlatten}, and pushing via \jscode{arrayPush} utilize the abstract
semantics.  This is the core idea of sealed symbolic execution to maximize the
part of dynamic analysis during static analysis.

In the remaining section we formally define the combined analysis with sealed
symbolic execution in Section~\ref{sec:formal}.  Then, we explain how to define
the combined analysis for JavaScript programs in Section~\ref{sec:javascript}.
